SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios

### 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex
make change according to Loen's comments

The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}. Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux ratios when compared to the results for the SIE-only model. 
% with a reduced $\chi^2 = 2.7$
The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model. The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.  {\bf In the NIR imaging there is no sign of a bulge; a formal bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.  We therefore interpret the mass in the ExpDisc component as the baryonic mass of lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models need the full extent of the gravitational arc for constraints. {\bf The extinction in the AO imaging is so severe that components B and D are not visible, and the arc that connects A and B appears to be truncated.  The low signal-to-noise ratio and the strong extinction prevent us from using modeling techniques that incorporate the extended NIR emission \citep[e.g.][]{V12}.  Future high resolution radio imaging is needed in order to place stronger constraints on the mass model.}

@@

{\bf Here, we find evidence for an edge-on disc in the flux-ratio
  anomaly gravitational lens B1555+375 that can also account for the
  required perturbation in the mass model. Such high-order deviations
  from a smooth mass distribution have already been suggested
  previously \citep{evans03, congdon05}, but this is the first time
  that an observed disc has been explicitly modelled to account for a
  flux-ratio anomaly. However, it is important to realise that by
  including observationally-motivated perturbations to a `smooth' mass
  distribution, such as luminous dwarf companions or edge-on discs, in
  the mass models, we are still limited in our interpretation since we
  must assume that the anomalies are due exclusively to these
  additional components.  For B1555+375, it may be possible to
  independently constrain the mass of the disc through kinematic
  measurements (most likely from mm-wavelength resolved emission line
  observations), which would test whether the disc makes a sufficient
  contribution to the mass model (e.g. as in the case of B1933+503;
  \citet{suyu12}). Also, as we have shown here, B1555+375 shows
  evidence for an extended $\sim$ 100 mas gravitational arc at radio
  wavelengths that crosses the edge-on disc. Further high resolution
  imaging with very long baseline interferometry will provide the
  observational constraints required to fully test whether the disc is
  sufficient to cause the anomaly.}

>>>>

The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}. Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux ratios when compared to the results for the SIE-only model. 
% with a reduced $\chi^2 = 2.7$
The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model. The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.  {\bf In the NIR imaging there is no sign of a bulge; a formal bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.  We therefore interpret the mass in the ExpDisc component as a good description of the baryonic mass of lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models need the full extent of the gravitational arc for constraints. {\bf The extinction in the AO imaging is so severe that components B and D are not visible, and the arc that connects A and B appears to be truncated.  The low signal-to-noise ratio and the strong extinction prevent us from using modeling techniques that incorporate the extended NIR emission \citep[e.g.][]{V12}.  Future high resolution radio imaging is needed in order to place stronger constraints on the mass model.}

@@

{\bf Here, we find evidence for an edge-on disc in the flux-ratio
  anomaly gravitational lens B1555+375 that can also account for the
  required perturbation in the mass model. Such high-order deviations
  from a smooth mass distribution have already been suggested
  previously \citep{evans03, congdon05}, but this is the first time
  that an observed disc has been explicitly modelled to account for a
  flux-ratio anomaly. However, it is important to realise that by
  including observationally-motivated additional components/modification[?] to a `smooth' mass
  distribution, such as luminous dwarf companions or edge-on discs, in
  the mass models, we are still limited in our interpretation since we
  must assume that the anomalies are due exclusively to these
  additional components.  For B1555+375, it may be possible to
  independently constrain the mass of the disc through kinematic
  measurements (most likely from mm-wavelength resolved emission line
  observations), which would test whether the disc makes a sufficient
  contribution to the mass model (e.g. as in the case of B1933+503;
  \citet{suyu12}). Also, in the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows
  evidence for an extended $\sim$ 100 mas gravitational arc at radio
  wavelengths that crosses the edge-on disc. Further high resolution
  imaging with very long baseline interferometry will provide the
  observational constraints required to fully test whether the disc is
  sufficient to cause the anomaly.}
